### 2016-07-14 version0.0/intro0.01.tex

A complete picture of how galaxies are formed and evolve is tied to unfolding the mystery of the formation of stars.
 Various phenomena affect the collapse of molecular clouds and star formation, including the environment of the star-forming region, chemical composition of the region, the initial density distribution of the gas and the mass of stars in galaxies.
 For decades, observational, theoretical and numerical studies have investigated star formation; nevertheless, their results are contrary.
 Empirical studies are used alongside theoretical ones to find laws that indicate the relations between physical properties of galaxies and star formation.

@@

In this thesis, we present three projects that study the effects of galaxy properties on star formation.
We use UV to radio observations of both nearby and high-redshift galaxies, measure their physical properties, and using modern statistical methods, study their impact on SFR.
Chapter~\ref{ch: paper1} focuses on investigating star formation laws in the Andromeda galaxy (M31) on both local and global scales using hierarchical Bayesian analysis.
In addition to the Kennicutt-Schmidt law, we study the extended Schmidt law~\citep{Shi11} and the metallicity/star formation correlation~\citep{Krumholz09}.
We also show the effect on star formation laws of using different SFR and ISM gas tracers.
In Chapter~\ref{ch: paper3}, we explore nearby galaxies using an unsupervised data-mining method (the self-organizing map, or SOM).
We cluster observational data to derive quantities of spatially resolved regions in M31 and examine the physical properties of each cluster.
During this process, we find hidden structures in high-dimensional data space.
In Chapter~\ref{ch: paper2}, we move to more distant galaxies and apply the SOM algorithm to their spectral energy distributions.
We train networks using a set of galaxy SED templates covering the wavelength range from UV to IR and use them to classify the SEDs of a sample of 142 galaxies with $0.5 < z < 1$. 
Then we study the grouped properties of the classified galaxies.
We summarize our results and discuss potential future work and applications of the results of this thesis in Chapter~\ref{ch: summary}

>>>>

A complete picture of how galaxies are formed and evolve is tied to unfolding the mystery of the formation of stars.
 Various phenomena affect the collapse of molecular clouds and star formation, including the environment of the star-forming region, chemical composition of the region, the initial density distribution of the gas and the mass of stars in galaxies.
 For decades, observational, theoretical and numerical studies have investigated star formation;  in many cases, their results disagree with each other.
 Empirical studies are used alongside theoretical ones to find laws that indicate the relations between physical properties of galaxies and star formation.

@@

In this thesis, we present three projects that study the effects of galaxy properties on star formation.
We use UV to radio observations of both nearby and high-redshift galaxies, measure their physical properties, and using modern statistical methods, study their impact on SFR.
Chapter~\ref{ch: paper1} focuses on investigating star formation laws in the Andromeda galaxy (M31) on both local and global scales using hierarchical Bayesian analysis.
In addition to the Kennicutt-Schmidt law, we study the extended Schmidt law~\citep{Shi11} and the metallicity/star formation correlation~\citep{Krumholz09}.
We also show the effect on star formation laws of using different SFR and ISM gas tracers.
In Chapter~\ref{ch: paper3}, we explore nearby galaxies using an unsupervised data-mining method (the self-organizing map, or SOM).
We cluster observational data to derive quantities of spatially resolved regions in M31 and examine the physical properties of each cluster.
During this process, we find hidden structures in high-dimensional data space.
In Chapter~\ref{ch: paper2}, we move to more distant galaxies and apply the SOM algorithm to their spectral energy distributions.
We train networks using a set of galaxy SED templates covering the wavelength range from UV to IR and use them to classify the SEDs of a sample of 142 galaxies with $0.5 < z < 1$. 
Then we study the grouped properties of the classified galaxies.
We summarize our results and discuss potential future work and applications of the results of this thesis in Chapter~\ref{ch: summary}.
